Experimentally Informed Site-Specific Substitution Models Substantially Deepen Viral Divergence Estimates

### 2018-01-22 manuscript/manuscript.tex
tweaks to figures
updated manuscript

\begin{figure}[H]
\centerline{\includegraphics[width=0.85\textwidth]{figures/doud_compete}}
\caption{\label{fig:doud_compete}
\textbf{The ExpCM defined by H1 preferences lengthen longer branches on the HA tree.} 
\textbf{(A)} An HA alignment was subsampled to create three smaller alignments with varying degrees of divergence from the focal H3 sequence, referred to as "low", "intermediate", and "high". 
\textbf{(B)} The phylogenetic tree of the "high" alignment. 
The colors denote the alignment and the black circle denotes the focal H3 sequence. 
\textbf{(C)} The value of the ExpCM and ExpCM+$\Gamma\omega$ stringency parameter $\beta$ decreases as the divergence from the focal H3 sequence increases. 
\textbf{(D)} Comparisons of branch lengths optimized by the four substitution models for the varying degrees of divergence. 
Black points represent branches from the focal H3 sequence and grey points represent all other branches.  
The branch lengths are in average number of codon substitutions per site. 
}
\end{figure}

@@

\begin{suppfig}[H]
\centerline{\includegraphics[width=\textwidth]{figures/prefs_doud}}
\caption{\label{suppfig:prefs_doud}
\textbf{H1 preferences measured by \cite{doud2016accurate} rescaled with the ExpCM stringency parameter optimized in \ref{fig:tree_doud}A  ($\beta = 1.54$)} 
}
\end{suppfig}

\begin{suppfig}[H]
\centerline{\includegraphics[width=\textwidth]{figures/prefs_lee}}
\caption{\label{suppfig:prefs_lee}
\textbf{H3 preferences measured by \textit{lee} rescaled with the ExpCM stringency parameter optimized in \ref{fig:tree_lee}A  ($\beta = 1.76$)} 
}
\end{suppfig}

\begin{figure}[H]
\centerline{\includegraphics[width=\textwidth]{figures/prefs_average}}
\caption{\label{fig:prefs_average}
\textbf{The average of the H1 preferences measured by \cite{doud2016accurate} and the H3 preferences measured by \textit{Lee} rescaled with the ExpCM stringency parameter optimized in \ref{fig:tree_average}A  ($\beta = 1.77$)}}
\end{figure}

@@

\begin{figure}[H]
\centerline{\includegraphics[width=0.85\textwidth]{figures/lee_competing}}
\caption{\label{fig:lee_compete}
\skhcomment{something weird is going on with the low alignment. I am going to go back and look at this.}
\textbf{The ExpCM defined by H1 preferences lengthen longer branches on the HA tree.} 
\textbf{(A)} An HA alignment was subsampled to create three smaller alignments with varying degrees of divergence from the focal H3 sequence, referred to as "low", "intermediate", and "high". 
\textbf{(B)} The phylogenetic tree of the "high" alignment. 
The colors denote the alignment and the black circle denotes the focal H3 sequence. 
\textbf{(C)} The value of the ExpCM and ExpCM+$\Gamma\omega$ stringency parameter $\beta$ decreases as the divergence from the focal H3 sequence increases. 
\textbf{(D)} Comparisons of branch lengths optimized by the four substitution models for the varying degrees of divergence. 
Black points represent branches from the focal H3 sequence and grey points represent all other branches.  
The branch lengths are in average number of codon substitutions per site. 
}
\end{figure}

>>>>

\begin{figure}[H]
\centerline{\includegraphics[width=0.85\textwidth]{figures/doud_compete_2}}
\caption{\label{fig:doud_compete}
\textbf{The ExpCM defined by H1 preferences lengthen longer branches on the HA tree.} 
\textbf{(A)} An HA alignment was subsampled to create three smaller alignments with varying degrees of divergence from the focal H3 sequence, referred to as "low", "intermediate", and "high". 
\textbf{(B)} The phylogenetic tree of the "high" alignment. 
The colors denote the alignment and the black circle denotes the focal H3 sequence. 
\textbf{(C)} The value of the ExpCM and ExpCM+$\Gamma\omega$ stringency parameter $\beta$ decreases as the divergence from the focal H3 sequence increases. 
\textbf{(D)} Comparisons of branch lengths optimized by the four substitution models for the varying degrees of divergence. 
Black points represent branches from the focal H3 sequence and grey points represent all other branches.  
The branch lengths are in average number of codon substitutions per site. 
}
\end{figure}

@@

\begin{suppfig}[H]
\centerline{\includegraphics[width=\textwidth]{figures/prefs_doud}}
\caption{\label{suppfig:prefs_doud}
\textbf{H1 preferences measured by \cite{doud2016accurate} rescaled with the ExpCM stringency parameter optimized in \ref{fig:tree_doud}A  ($\beta = 1.19$)} 
\skhcomment{I need to change the $\beta$ value when the new \texttt{phydms} results finish running.}
}
\end{suppfig}

\begin{suppfig}[H]
\centerline{\includegraphics[width=\textwidth]{figures/prefs_lee}}
\caption{\label{suppfig:prefs_lee}
\textbf{H3 preferences measured by \textit{lee} rescaled with the ExpCM stringency parameter optimized in \ref{fig:tree_lee}A  ($\beta = 1.46$)}
\skhcomment{I need to change the $\beta$ value when the new \texttt{phydms} results finish running.} 
}
\end{suppfig}

\begin{figure}[H]
\centerline{\includegraphics[width=\textwidth]{figures/prefs_average}}
\caption{\label{fig:prefs_average}
\textbf{The average of the H1 preferences measured by \cite{doud2016accurate} and the H3 preferences measured by \textit{Lee} rescaled with the ExpCM stringency parameter optimized in \ref{fig:tree_average}A  ($\beta = 1.77$)}}
\skhcomment{I need to change the $\beta$ value when the new \texttt{phydms} results finish running.}
\end{figure}

@@

\begin{suppfig}[H]
\centerline{\includegraphics[width=0.85\textwidth]{figures/lee_compete}}
\caption{\label{fig:lee_compete}
\textbf{The ExpCM defined by H1 preferences lengthen longer branches on the HA tree.} 
\textbf{(A)} An HA alignment was subsampled to create three smaller alignments with varying degrees of divergence from the focal H3 sequence, referred to as "low", "intermediate", and "high". 
\textbf{(B)} The phylogenetic tree of the "high" alignment. 
The colors denote the alignment and the black circle denotes the focal H3 sequence. 
\textbf{(C)} The value of the ExpCM and ExpCM+$\Gamma\omega$ stringency parameter $\beta$ decreases as the divergence from the focal H3 sequence increases. 
\textbf{(D)} Comparisons of branch lengths optimized by the four substitution models for the varying degrees of divergence. 
Black points represent branches from the focal H3 sequence and grey points represent all other branches.  
The branch lengths are in average number of codon substitutions per site. 
}
\end{suppfig}
